\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
Starting to rewrite scientific relevance section

This project is accompanied by a scientific study. The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system and how to improve these interactions. The focus hereby is on the usability of an ubiquitous health tracking system that (half-)automatically generates useful data of the habits of the participants. This data should lead to a good basis for future work on the topic. \\
% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}

@@

%\note{
%\begin{itemize}
%\item {\em Length: 1-2 pages}
%\item Why is the project scientifically interesting?
%\item Did others point out that this is an open question?
%\item What are the innovative aspects that make it interesting?
%\item How could the project break new ground scientifically?
%\item To what extent are the objectives ambitious and beyond the state of the art (e.g. novel concepts and approaches or development across disciplines)?
%\end{itemize}
%}
\subsection{Scientifical point of view}

The approach to create a game out of tasks for sick people is not new. Dealing with traumatized children by example is nowadays often combined with a game. There are several different developments of games to fit the needs of different patients and problem fields. Furthermore there are very successful social gamifications like "Foursquare" \footnote{\url{https://foursquare.com/about/}} where people check in to places and earn achievements. All of that to keep track of what friends are doing. There is a high scientific potential in our idea because it combines many of already given approaches with existing infrastructure and organizations. For example a hospital can keep track of their patients health status after surgeries or treatments remote. A good idea would be to use the gathered data for better observation of diabetics. Hardware to gather the additional data is already available (see \footnote{\url{http://www.bgstar.com/web/ibgstar}}). These possibilities to collect data lead to more knowledge of different diseases and effectiveness of treatments. By example collection the data of stuff people eat and how much they do physical workouts combined with the actual disease can help creating specialized therapies and new approaches to improve existing ones.\\

>>>>

This project is accompanied by a scientific study. The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system and how to improve these interactions. The focus hereby is on the usability of an ubiquitous health tracking system that (half-)automatically generates useful data of the habits of the participants. This data should lead to a good basis for future work on the topic. \\

% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}

@@

%\note{
%\begin{itemize}
%\item {\em Length: 1-2 pages}
%\item Why is the project scientifically interesting?
%\item Did others point out that this is an open question?
%\item What are the innovative aspects that make it interesting?
%\item How could the project break new ground scientifically?
%\item To what extent are the objectives ambitious and beyond the state of the art (e.g. novel concepts and approaches or development across disciplines)?
%\end{itemize}
%}

\subsection{Scientifical point of view}
Using gamification as a motivational factor isn‘t new, there are several systems and successful gamifications like $"Foursquare"$ \footnote{\url{https://foursquare.com/about/}} on the market. See \ref{sect:star} for a list of other systems using gamification in a health-related environment. The modern health care system is scientifically interesting because it combines several well-known approaches into a new interconnected system and it is unknown if and how such a system can work. There is a high scientific potential in our idea because it combines many of already given approaches with existing infrastructure and organizations. The modern health care system is on the one hand a psychological study on how gamification of everydays tasks can influence peoples behaviour, on the other hand it tries to gather new knowledge in the field of ubiquitous computing, usability and security/privacy. There are several questions we try to answer, see \ref{sect:goals} for an exhaustive list.

It is already known that gamification, achievements and rankings can boost people's motivation. The questions we try to answer are whether gamification of simple tasks can lead to a long-term improvement of peoples attitude towards health. By using several sources for tracking we can gather more data than any other system already on the market and can therefore generate much more accurate data that is needed to answer those questions. The term \emph{ubiquitous computing} was first mentioned by Mark Weiser in 1988 and was shaped in his paper \emph{The computer for the 21st century} \cite{weiser99}. Since then ubiquitous computing became a trending form of computing which we believe will play a more and more important role in the future. The modern health care system tries to make use of ubiquitous computing in a broad range and therefore tries to push the integration of computing in day-to-day tasks and this new form of human computer interaction. By using an integrated system for health tracking on such a broad range ubiquitous computing can be pushed to its limits, since we need to track data from several forms of sources and sensors and this from a statistically relevant number of people. \\
